---
title: "Weight of Fish"
author: "Esteffani Maldonado"
date: "Fall 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
mydata <- read.csv(file = "Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

```{r}
library(leaps)
regsubsets.out <- 
  regsubsets(Weight ~ .,
             data=perch, 
             nbest = 1,  # 1 best model for each number of predictors  
             nvmax = NULL,  # Null for no limit on number of variables
             force.in = NULL, force.out = NULL,
             method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright",main="Adjusted R^2")
```

```{r}
perchMODL <- lm(Weight~ Height+Width, data=perch)
summary.lm(perchMODL)
```
  
The Height and Width variables compose the best two regression model to predict the weight of the perch. The adjusted R-squared of the regression model is 0.94. 
  
# Pike

```{r}
Pike <- filter(mydata, Species == "Pike")
Pike <- select(Pike, -Species)
```

```{r}
library(leaps)
regsubsets.out <- 
  regsubsets(Weight ~ .,
             data = Pike,
             nbest = 1,      # 1 best model for each number of predictors
             nvmax = NULL,  # NULL for no limit on number of variables
             force.in = NULL, force.out = NULL, 
             method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright", main="Adjusted R^2")
```


```{r}
PikeMODL <- lm(Weight~ Length1+Length3,data=Pike)
summary.lm(PikeMODL)
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
