---
title: "Weight of Fish"
author: "Esteffani Maldonado"
date: "Fall 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
mydata <- read.csv(file = "Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

```{r}
library(leaps)
regsubsets.out <- 
  regsubsets(Weight ~ .,
             data=perch, 
             nbest = 1,  # 1 best model for each number of predictors  
             nvmax = NULL,  # Null for no limit on number of variables
             force.in = NULL, force.out = NULL,
             method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright",main="Adjusted R^2")
```

```{r}
perchMODL <- lm(Weight~ Height+Width, data=perch)
summary.lm(perchMODL)
```
  
The Height and Width variables compose the best two regression model to predict the weight of the perch. The adjusted R-squared of the regression model is 0.94. 
  
# Pike

```{r}
Pike <- filter(mydata, Species == "Pike")
Pike <- select(Pike, -Species)
```

```{r}
library(leaps)
regsubsets.out <- 
  regsubsets(Weight ~ .,
             data = Pike,
             nbest = 1,      # 1 best model for each number of predictors
             nvmax = NULL,  # NULL for no limit on number of variables
             force.in = NULL, force.out = NULL, 
             method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright", main="Adjusted R^2")
```


```{r}
PikeMODL <- lm(Weight~ Length1+Length3,data=Pike)
summary.lm(PikeMODL)
```

To predict the weight of Pike, the best regression model would use the Length1 and Length3 variables with an adjusted R-squared of 0.9649. However, the best regression model overall would be the model that includes all the variables.


# Roach

```{r}
Roach <- filter(mydata, Species == "Roach")
Roach <- select(Roach, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight~ .,
             data = Roach, 
             nbest = 1,    # 1 best model for each number of predictors
             nvmax = NULL, # NULL for no limit on number variables
             force.in = NULL, force.out = NULL, 
             method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out, statistic="adjr2", legend="bottomright",main="AdjustedR^2")

```
  
```{r}
RoachMODL <- lm(Weight~ Length3+Width, data=Roach)
summary.lm(RoachMODL)
```
  
The best two variable regression model to predict the weight of Roach uses the Length3 and Width variables. The Adjusted R-squared is 0.8482.
  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
  
```{r}
basicNN <- ggplot(perch,aes(y=Weight, x=Width))
basicNN + geom_point() + geom_smooth(method=lm) + ggtitle("Perch")
```
  
Above is the graph for the Perch regression model using the variables Weight and Width. 
  

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We used charts that compared the adjusted R-squared for each two variable regression model for each respective type of fish, perch, pike, and roach. From each of these charts, we were able to conclude that the best model to find the weight of perch would have the Height and Weight variables. The best model to find the weight of pike would use the Length1 and Length3 variables. Finally the best regression model to find the weight of roach would use the Length3 and the Width variables. 


